A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-02-15 papers/execution-model/model.tex
semantics and typing of originate fixed
sync
abstract, intro, and start of motivation

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{fixme}
\usepackage{listings}
\usepackage{xcolor}

\input{macros}

@@

\begin{document}
\maketitle
\pagestyle{plain}
\begin{abstract}
  Smart contract applications on the blocking can only reach their full potential if
  they can be integrated with traditional software systems. Invoking
  contracts and observing the state of the blockchain requires a
  programmatic interface. We propose a typed API for this
  purpose and establish some properties of the combined
  system. Specifically, we provide an execution model that
  enables us to prove type-safe interaction between programs and the 
  blockchain. We establish further properties of the model that
  translate into requirements on the API. A prototype of the interface
  is implemented in OCaml for the Tezos blockchain.
\end{abstract}

@@

An auctioneer wants to run an auction on the blockchain using a smart
contract. Once to the contract is deployed on the blockchain, the
auction is open for bidding, but it should be closed after 48 hours,
say. Bidding on the auction and closing the auction are two different
entrypoints / methods of the auction contract.

While it is acceptable for the auctioneer to deploy the contract manually, it
is desirable to have a mechanism that reliably closes the auction
after 48 hours have passed. So the auctioneer wants to write a program
to do so.

On the other side, a bidder may want to implement a certain bidding
strategy that starts at a certain amount and increases the bid until a
certain limit is reached. Of course, the bidder only increases if
someone else placed a higher bid. So the bidder also wants to write a
program to implement this strategy.

Both tasks cannot be implemented as smart contracts because they react
to external triggers. Closing requires
to schedule the activation of a contract at a certain time and bidding
requires to watch the state of the contract (current highest bid) and
react if another bidder places a higher bid.

Let us consider how this auction contract could be written in Michelson, the language of smart contracts in Tezos. The state of a smart contract is presented in its storage on the blockchain. The input data provided with a contract invocation is specified as a parameter.

\begin{lstlisting}[numbers=none]
parameter (or (unit %close)
              (mutez %bid)); # participant's bid
storage (pair
              (pair bool address)  # is bidding allowed,
               contract owner's address
              (pair mutez address) # current highest bid
               and bidder's address
        );
\end{lstlisting}
where \texttt{unit} is the type whose only value is \texttt{Unit}, \texttt{mutez} is a specific type for tokens in Tezos, and \texttt{pair} is a pair of values a and b of types (l) and (r) written as (\texttt{Pair a b}).

@@

\begin{lstlisting}[numbers=none]
address = orinigate-contract(script);
Time.sleep(to-second(48));
call-contract(address, Unit);
\end{lstlisting}
where \texttt{script} is the contract's script and \texttt{to-second} function converts hour to second.

@@

\begin{definition}%[Query]
\emph{Queries} are defined by the following grammar:
\begin{align*}
  \QRY & ::=
  \GETCOUNTER\PUK  
  \\&\mid \GETBALANCE\ADDR
  \\&\mid \GETSTATUS\OPH
  \\&\mid \GETSTORAGE\PUH
  \\&\mid \GETCODE\PUH 
  \\&\mid \GETTYPE\PUH
\end{align*}
\end{definition}

\begin{definition}%[Program]
\emph{Expressions} are defined by the following grammar:
\begin{align*}
  \CONSTANT & ::= \INT %\mid \ADDR
              \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
              \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\INT) \mid
            \STATUSTIMEOUT \\
  \ERROR &::= \ERRPRG \mid \ERRBAL \mid \ERRCOUNT \mid \ERRFEE \mid
           \ERRPUK \mid \ERRPUH \mid \ERRARG \mid \ERRINIT\\
	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \ERROR \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
	\mid \EXPR\EXPR \mid (\EXPR,\EXPR) \mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
	\\&\mid \EXPR\ \PLUS\ \EXPR\ \mid \EXPR\ \MINUS\ \EXPR\ \mid \EXPR\ \EQUAL\ \EXPR\ \mid \EXPR\ \LESS\ \EXPR
	\\&\mid \EXPR\ \AND\ \EXPR\ \mid \EXPR\ \OR\ \EXPR\ \mid \NOT\ \EXPR
  \\&\mid \NIL\ \mid \CONS\ \EXPR\ \EXPR \mid \LEFT\ \EXPR \mid\RIGHT\
  \EXPR \mid \SOME\ \EXPR \mid \NONE
  \\& \mid \RAISE\ \EXPR \mid \TRY\ \EXPR\ \EXCEPT\ \EXPR
  \\& \mid \MATCH\ \EXPR\ \WITH\ \PATTERN\to\EXPR \dots
  \\& \mid \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR
  \\& \mid \ORIGINATE\EXPR\EXPR\EXPR\EXPR\EXPR
  \\&\mid \QOP\  \EXPR\\
  \QOP & ::= balance \mid status \mid storage \mid code \mid counter \mid type
\end{align*}
We let $\EXPRS$ range over sets of expressions.

@@

Example pseudo code
\begin{align*}
  \OPH &=  \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR \\
       & \MATCH\ {status\ \OPH}\ \WITH \\
       & \mid \STATUSPENDING \to \textrm{not yet included, continue waiting} \\
       & \mid \STATUSINCLUDING (n) \to \textrm{included with $n$
         blocks confirmation}\\
       & \mid \STATUSTIMEOUT \to \textrm{lost, try again}
\end{align*}
Grammar of types
\begin{align*}
  \TYPE, \TYPEU & ::= \TADDR \mid \TOPH \mid \TPUH\ \TYPE\ \TYPEU \mid
                  \TPUK \mid
                  \TCODE\ \TYPE\ \TYPEU \mid \TTEZ \mid
          \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TSTATUS \\
  & \mid \TYPE\to\TYPEU \mid \TPAIR\ \TYPE\ \TYPEU \mid \TLIST\ \TYPE
    \mid \TSUM\ \TYPE\ \TYPEU \mid \TOPTION\ \TYPE \mid \TEXCEPTION
\end{align*}

@@

  \inferrule{}{\JTypeExpr\TEnv\PUH{\TPUH\ ?\ ?}}

@@

@@

  \inferrule{
    \JTypeExpr\TEnv\EXPR\TYPE \\
    \JTypeExpr\TEnv{\EXPR'}{\TEXCEPTION\to\TYPE}
  }{
    \JTypeExpr\TEnv{\TRY\ \EXPR\ \EXCEPT\ \EXPR'}\TYPE
  }
  \\\\
  % too generic
  % \inferrule{
  %   \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
  %   \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
  %   \JTypeExpr\TEnv{\EXPR_3}\TADDR \\
  %   \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
  %   \JTypeExpr\TEnv{\EXPR_5}\TTEZ
  % }{
  %   \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
  % }
  %   
  \inferrule{
    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
    \JTypeExpr\TEnv{\EXPR_3}\TPUK \\
    % \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
  }{
    \JTypeExpr\TEnv{\TRANSFER{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
  }

  \inferrule{
    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
    \JTypeExpr\TEnv{\EXPR_3}\TPUH\ \TYPE_p\ \TYPE_s \\
    \JTypeExpr\TEnv{\EXPR_4}{\TYPE_p} \\
    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
  }{
    \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
  }

  \inferrule{
    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
    \JTypeExpr\TEnv{\EXPR_3}{\TCODE\ (\TPAIR\ \TYPE_p\ \TYPE_s)} \\
    \JTypeExpr\TEnv{\EXPR_4}\TYPE_s \\ % really \TSTRING \\
    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
  }{
    \JTypeExpr\TEnv{\ORIGINATE{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_4}{\EXPR_5}}{
      \TPUH\ \TYPE_p\ \TYPE_s} 
  }
\end{mathpar}

@@

@@

\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \PUH = \GENERATEHASH(\CODE, \TIME) \\
    \TIME-\hat\TIME  \le 60
  }{
      [\EC{\OPH}  :: \EXPRS, \ACCOUNTS] \| [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    \SystemTrans \\
     [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
  }
\end{mathpar}

>>>>

\documentclass[a4paper]{llncs}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{mathpartir}
\usepackage{fixme}
\usepackage{xcolor}
\usepackage{listings}
\lstdefinelanguage{michelson}{
%  basicstyle=\ttfamily,
  morekeywords={parameter,storage,or,unit,mutez,pair,bool,address}, sensitive=false,
  morecomment=[l]{\#},
  morecomment=[s]{/*}{*/},
  morestring=[b]",
}
\lstset{language=michelson}
\input{macros}

@@

\begin{document}
\maketitle
\pagestyle{plain}
\begin{abstract}
  Smart contract applications on the block chain can only reach their full potential if
  they can be integrated with traditional software systems. Invoking
  contracts and observing the state of the blockchain requires a
  programmatic interface. We propose a typed API for this
  purpose and establish some properties of the combined
  system. Specifically, we provide an execution model that
  enables us to prove type-safe interaction between programs and the 
  blockchain. We establish further properties of the model that
  give rise to requirements on the API. A prototype of the interface
  is implemented in OCaml for the Tezos blockchain.
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Smart contracts rarely live in isolation. To reach their full
potential, it should be possible to integrate them with traditional
software systems and to enable input from outside the blockchain. Such
input requires trusted intermediaries that run so-called oracles \cite{oracles}. A
smart contract registers a request and a callback with an oracle. The
oracle invokes the callback as soon as an answer is available.

We present two examples where integration of smart contracts is needed
and propose a typed API for making such integration type safe.

@@

Suppose you want to run an auction on the blockchain using a smart
contract. Once to the contract is deployed, the
auction is open for bidding, but it should be closed after 48 hours,
say. Such a timeout is a typical task for an oracle. Rather than
trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
after 48 hours have passed. So you want to write a program to do so.

As a bidder, you may want to implement a bidding
strategy that starts at a certain amount and increases the bid until a
limit is reached. Of course, you only want to increase if
someone else placed a higher bid. So you also want to write a
program to implement this strategy.

Neither task can be implemented as a smart contract alone because they react
to external triggers. Closing requires to schedule the activation of a
contract at a certain time and bidding 
requires to watch the current highest bid of the contract and
react if another bidder places a higher bid.

For concreteness, Listing~\ref{lst:auction-contract-header} shows the
header of an auction contract in Michelson \cite{michelson}. The
\lstinline/parameter/ clause specifies the contract's parameter
type. It is a sum type (indicated by \lstinline/or/) and each
alternative constitutes an entrypoint, named \lstinline/%close/ and
\lstinline/%bid/. Entrypoint \lstinline/%close/ takes a \texttt{unit}
parameter and \lstinline/%bid/ takes an amount of tokens \texttt{mutez}.
The \lstinline/storage/ clause declares the state of the contract,
which is a nested pair type indicating whether bidding is allowed, the address of the
contract owner (to prohibit unauthorized calls to \lstinline/%close/),
the highest bid, and the bidder's address.
\begin{lstlisting}[numbers=none,float,caption={Header of the auction contract},label={lst:auction-contract-header},captionpos=b,emph={close,bid},emphstyle=\underbar]
parameter (or (unit %close)
              (mutez %bid)); # participant's bid
storage (pair
          (pair bool address)  # bidding allowed, contract owner
          (pair mutez address) # highest bid, bidder's address
        );
\end{lstlisting}

@@

\begin{lstlisting}[numbers=none]
address = originate-contract(script);
Time.sleep(to-second(48));
call-contract(address, Unit);
\end{lstlisting}
where \texttt{script} is the contract's script and \texttt{to-second} function converts hour to second.

@@

\begin{definition}%[Query]
\emph{Queries} are defined by the following grammar:
\begin{align*}
  \QRY & ::=
  \GETCOUNTER\PUK  
  \\&\mid \GETBALANCE\ADDR
  \\&\mid \GETSTATUS\OPH
  \\&\mid \GETSTORAGE\PUH
  % \\&\mid \GETCODE\PUH 
  % \\&\mid \GETTYPE\PUH
  \\&\mid \GETCONTRACT\OPH
\end{align*}
\end{definition}

\begin{definition}%[Program]
\emph{Expressions} are defined by the following grammar:
\begin{align*}
  \CONSTANT & ::= \INT %\mid \ADDR
              \mid \OPH \mid \PUH \mid\PUK \mid \CODE \mid
              \NTEZ \mid \SUNIT \mid \FALSE \mid \TRUE \\
  \STATUS & ::= \STATUSPENDING \mid \STATUSINCLUDING (\INT) \mid
            \STATUSTIMEOUT \\
  \ERROR &::= \ERRPRG \mid \ERRBAL \mid \ERRCOUNT \mid \ERRFEE \mid
           \ERRPUK \mid \ERRPUH \mid \ERRARG \mid \ERRINIT\\
	\EXPR & :: =  \CONSTANT \mid \STATUS \mid \ERROR \mid \VARIABLE \mid \lambda \VARIABLE. \EXPR\ 
	\mid \EXPR\EXPR \mid (\EXPR,\EXPR) \mid \FST\ \EXPR \mid \SND\ \EXPR 	%\mid \NI \EI
	\\&\mid \EXPR\ \PLUS\ \EXPR\ \mid \EXPR\ \MINUS\ \EXPR\ \mid \EXPR\ \EQUAL\ \EXPR\ \mid \EXPR\ \LESS\ \EXPR
	\\&\mid \EXPR\ \AND\ \EXPR\ \mid \EXPR\ \OR\ \EXPR\ \mid \NOT\ \EXPR
  \\&\mid \NIL\ \mid \CONS\ \EXPR\ \EXPR \mid \LEFT\ \EXPR \mid\RIGHT\
  \EXPR \mid \SOME\ \EXPR \mid \NONE
  \\& \mid \RAISE\ \EXPR \mid \TRY\ \EXPR\ \EXCEPT\ \EXPR
  \\& \mid \MATCH\ \EXPR\ \WITH\ \PATTERN\to\EXPR \dots
  \\& \mid \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR
  \\& \mid \ORIGINATE\EXPR\EXPR\EXPR\EXPR\EXPR
  \\&\mid \QOP\  \EXPR \mid \CONTRACT\ \TYPE\ \EXPR \mid \TOSTRING\
  \EXPR \mid \FROMSTRING\ \TYPE\ \EXPR\\
  \QOP & ::= balance \mid status \mid storage \mid code \mid counter \mid type
\end{align*}
We let $\EXPRS$ range over sets of expressions.

@@

Example pseudo code
\begin{align*}
  \OPH &=  \TRANSFER[\EXPR]\EXPR\EXPR\EXPR\EXPR \\
       & \MATCH\ {status\ \OPH}\ \WITH \\
       & \mid \STATUSPENDING \to \textrm{not yet included, continue waiting} \\
       & \mid \STATUSINCLUDING (n) \to \textrm{included with $n$
         blocks confirmation}\\
       & \mid \STATUSTIMEOUT \to \textrm{lost, try again}
\end{align*}
Grammar of types
\begin{align*}
  \TYPE, \TYPEU & ::= \TADDR \mid \TOPH \mid
                  \TCONTRACT\ \TYPE \mid
                  % \TPUH\ \TYPE \mid
                  \TPUK \mid
                  \TCODE\ \TYPE\ \TYPEU \mid \TTEZ \mid
          \TINT \mid \TUNIT \mid \TBOOL \mid \TSTRING \mid \TSTATUS \\
  & \mid \TYPE\to\TYPEU \mid \TPAIR\ \TYPE\ \TYPEU \mid \TLIST\ \TYPE
    \mid \TSUM\ \TYPE\ \TYPEU \mid \TOPTION\ \TYPE \mid \TEXCEPTION
\end{align*}

@@

  \inferrule{}{\JTypeExpr\TEnv\PUH{\TADDR}}

@@

  \inferrule{\JTypeExpr\TEnv\EXPR\TADDR}{\JTypeExpr\TEnv{\CONTRACT\ \TYPE\ \EXPR}{\TOPTION
      (\TCONTRACT\ \TYPE)}}

@@

  \inferrule{
    \JTypeExpr\TEnv\EXPR\TYPE \\
    \JTypeExpr\TEnv{\EXPR'}{\TEXCEPTION\to\TYPE}
  }{
    \JTypeExpr\TEnv{\TRY\ \EXPR\ \EXCEPT\ \EXPR'}\TYPE
  }
  \\\\
  % too generic
  % \inferrule{
  %   \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
  %   \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
  %   \JTypeExpr\TEnv{\EXPR_3}\TADDR \\
  %   \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
  %   \JTypeExpr\TEnv{\EXPR_5}\TTEZ
  % }{
  %   \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
  % }
  %   
  \inferrule{
    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
    % \JTypeExpr\TEnv{\EXPR_3}\TPUK \\
    \JTypeExpr\TEnv{\EXPR_3}{\TCONTRACT\ \TUNIT} \\
    % \JTypeExpr\TEnv{\EXPR_4}\TSTRING \\
    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
  }{
    \JTypeExpr\TEnv{\TRANSFER{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
  }

  \inferrule{
    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
    \JTypeExpr\TEnv{\EXPR_3}\TCONTRACT\ \TYPE \\
    \JTypeExpr\TEnv{\EXPR_4}{\TYPE} \\
    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
  }{
    \JTypeExpr\TEnv{\TRANSFER[\EXPR_4]{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_5}}\TOPH
  }

  \inferrule{
    \JTypeExpr\TEnv{\EXPR_1}\TTEZ \\
    \JTypeExpr\TEnv{\EXPR_2}\TPUK \\
    \JTypeExpr\TEnv{\EXPR_3}{\TCODE\ \TYPE_p\ \TYPE_s} \\
    \JTypeExpr\TEnv{\EXPR_4}\TYPE_s \\ % really \TSTRING \\
    \JTypeExpr\TEnv{\EXPR_5}\TTEZ
  }{
    \JTypeExpr\TEnv{\ORIGINATE{\EXPR_1}{\EXPR_2}{\EXPR_3}{\EXPR_4}{\EXPR_5}}\TOPH 
  }
\end{mathpar}

Types for queries
\begin{mathpar}
  \inferrule{
    \JTypeExpr\TEnv\EXPR\TPUK
  }{
    \JTypeExpr\TEnv {\QRY\ \GETCOUNTER\EXPR}\TINT
  }

  \inferrule{
    \JTypeExpr\TEnv\EXPR\TADDR
  }{
    \JTypeExpr\TEnv {\QRY\ \GETBALANCE\EXPR}\TTEZ
  }

  \inferrule{
    \JTypeExpr\TEnv\EXPR\TOPH
  }{
    \JTypeExpr\TEnv {\QRY\ \GETSTATUS\EXPR}\TSTATUS
  }

  \inferrule{
    \JTypeExpr\TEnv\EXPR{\CONTRACT\ \TYPE}
  }{
    \JTypeExpr\TEnv {\QRY\ \GETSTORAGE\EXPR}\TSTRING
  }

  % \inferrule{
  %   \JTypeExpr\TEnv\EXPR{\CONTRACT\ \TYPE}
  % }{
  %   \JTypeExpr\TEnv {\QRY\ \GETCODE\EXPR}?
  % }
  %   
  % \inferrule{
  %   \JTypeExpr\TEnv\EXPR{\CONTRACT\ \TYPE}
  % }{
  %   \JTypeExpr\TEnv {\QRY\ \GETTYPE\EXPR}?
  % }
  %   
  \inferrule{
    \JTypeExpr\TEnv\EXPR{\TOPH}
  }{
    \JTypeExpr\TEnv {\QRY\ \GETCONTRACT\EXPR}\TPUH
  }
\end{mathpar}

Conversion to and from serialized storage; deserialization may fail
with an exception
\begin{mathpar}
  \inferrule{
    \JTypeExpr\TEnv\EXPR\TYPE \\
    \SERIALIZABLE (\TYPE)
  }{
    \JTypeExpr\TEnv{\TOSTRING\ \EXPR}\TSTRING
  }

  \inferrule{
    \JTypeExpr\TEnv{\EXPR}\TSTRING
  }{
    \JTypeExpr\TEnv{\FROMSTRING\ \TYPE\ \EXPR}\TYPE
  }
\end{mathpar}

@@

\subsection{Special reductions}
\label{sec:special-reductions}

\begin{mathpar}
  \inferrule[Contract?]{
    \JTypeCode\CODE{\TPAIR\ \TYPE\ \TYPEU} \\
    \BLOCKCHAIN.\CONTRACTORS (\PUH) =  \Angle{\CODE, \tilde\TIME, \NTEZ', \STRING'}
    %
    }{
    { [\EC{\CONTRACT\ \TYPE\ \PUH}  :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
    \SystemTrans
    { [\EC{\SOME\ \PUH} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
   }
  }

  \inferrule[Contract-Implicit?]{
    \PUK \in \DOM(\BLOCKCHAIN.\MANAGERS)
    %
    }{
    { [\EC{\CONTRACT\ \TUNIT\ \PUK}  :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
    \SystemTrans
    { [\EC{\SOME\ \PUK} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
   }
  }

  \inferrule[Contract-No?]{
    \ADDR \in \DOM (\BLOCKCHAIN.\MANAGERS) \Rightarrow \TYPE\ne\TUNIT \\
    \BLOCKCHAIN.\CONTRACTORS (\ADDR) = \Angle{\CODE, \tilde\TIME,
      \NTEZ', \STRING'} \Rightarrow {}
        \JTypeCode\CODE{\TPAIR\ \TYPE'\ \TYPEU} \wedge \TYPE \ne \TYPE' \\
    }{
    { [\EC{\CONTRACT\ \TYPE\ \ADDR}  :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
    }
    \SystemTrans
    { [\EC{\NONE} :: \EXPRS, \ACCOUNTS] \|
      \BLOCKCHAIN
   }
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \PUH = \GENERATEHASH(\CODE, \TIME) \\
    \TIME-\hat\TIME  \le 60
  }{
    [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSPENDING} :: \PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    \BlockTrans \\
     [\OPH \mapsto \Angle{\OP, \hat\TIME, \STATUSINCLUDING\ \TIME} :: \PENDING, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ),\\ \PUH \mapsto  \Angle{\CODE, \TIME, \NTEZ, \STRING} :: \CONTRACTORS, \TIME+1]
  }
\end{mathpar}
\begin{mathpar}
  \inferrule[Block-Accept-Query]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \PENDING (\OPH) =  \Angle{\OP,
       \hat\TIME, \STATUSINCLUDING\ \tilde\TIME} \\
    \CONTRACTORS (\PUH) =  \Angle{\CODE, \tilde\TIME, \NTEZ', \STRING'}
  }{
      [\EC{\QRY\ \GETCONTRACT\ \OPH}  :: \EXPRS, \ACCOUNTS] \| [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
    \SystemTrans 
     [\EC{ \PUH}  :: \EXPRS, \ACCOUNTS] \|  [\PENDING, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
